Code for Breast Cancer Pain Study

### 2020-07-26 manuscript_code_20200722.Rmd
tables

```{r,echo=FALSE}
library(openxlsx)
library(lattice)
library(quantreg)
library(ggplot2)
library(pscl)
library(boot)
library(MASS)
library(sjPlot)
library(nonnest2)
library(vcd)
library(AER)
library(faraway)
library(tidyverse)
library(table1)
library(RColorBrewer)
# library(ggpubr)

@@

dmd.pvt = dmd.pvt[-which(dmd.pvt$Poverty>70),]
dmd.pvt = dmd.pvt[-which((dmd.pvt$Vacancy>40) & (dmd.pvt$mean.Pain<2)),]
cat(paste("Three outliers excluded"),"\n")

@@

```{r,echo=FALSE,eval=FALSE}
xlist = c("Poverty.f","marital.status.f","Primary.Payer.f2","Usual.Occupation.f2","race.f","stage.f","age.f","chemo.f","surgery.f")

x = xlist[1]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[2]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[3]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",
               color = x, palette="jco")
p + stat_compare_means()

@@

```{r,echo=FALSE,eval=FALSE}
## Figure code - boxplot

x = "Poverty"
tmp = cdmd.pvt[,c("Pain","Poverty.f")]
colnames(tmp) = c("Pain",x)
tmp$Poverty = factor(tmp$Poverty)
tmp$Poverty = relevel(tmp$Poverty,"low")
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Marital.Status"
tmp <-
  cdmd.pvt %>%
  filter(marital.status.f2 %in% c("Married","Single")) %>%
  select("Pain","marital.status.f2")
colnames(tmp) = c("Pain",x)
class(tmp[,2])
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Primary.Payer"
tmp <-
  cdmd.pvt %>%
  filter(Primary.Payer.f2 %in% c("Insurance","Medicaid")) %>%
  select("Pain","Primary.Payer.f2")

colnames(tmp) = c("Pain",x)
class(tmp[,2])

base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))

ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Occupation"
tmp <-
  cdmd.pvt %>%
  filter(Usual.Occupation.f2 %in% c("Employed","Retired","Unemployed")) %>%
  select("Pain","Usual.Occupation.f2")

colnames(tmp) = c("Pain",x)
class(tmp[,2])

my_comparisons <- list( c("Employed", "Retired"), c("Retired", "Unemployed"), c("Employed", "Unemployed") )
base <- ggboxplot(tmp, x=x, y="Pain",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 15) +
  stat_compare_means(comparisons = my_comparisons, aes(label = ..p.signif..),hide.ns=T)

p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

>>>>

```{r,echo=FALSE}
library(openxlsx)
library(lattice)
library(quantreg)
library(ggplot2)
library(pscl)
library(boot)
library(MASS)
library(sjPlot)
library(nonnest2)
library(vcd)
library(AER)
library(faraway)
library(tidyverse)
library(table1)
library(RColorBrewer)
library(ggpubr)

@@

dmd.pvt = dmd.pvt[-which(dmd.pvt$Poverty>70),]
# dmd.pvt = dmd.pvt[-which((dmd.pvt$Vacancy>40) & (dmd.pvt$mean.Pain<2)),]
cat(paste("Three outliers excluded"),"\n")

@@

```{r,echo=FALSE,eval=FALSE}
xlist = explvars[4:length(explvars)]

x = xlist[1]
p <- ggboxplot(final.data, x=x, y="Pain",remove="Unknown",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[2]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",remove="Unknown",
               color = x, palette="jco")
p + stat_compare_means()

x = xlist[3]
p <- ggboxplot(cdmd.pvt, x=x, y="Pain",remove="Unknown",
               color = x, palette="jco")
p + stat_compare_means()

@@

```{r,echo=FALSE,eval=FALSE}
## Figure code - boxplot
xlist = explvars[4:length(explvars)]

# x = "Poverty"
# tmp = cdmd.pvt[,c("Pain","Poverty.f")]
# colnames(tmp) = c("Pain",x)
# tmp$Poverty = factor(tmp$Poverty)
# tmp$Poverty = relevel(tmp$Poverty,"low")
# base <- ggboxplot(tmp, x=x, y="Pain",
#                   color = x, palette="jco",legend="none") +
#   labs(x = NULL, y = "Pain", title = x) + 
#   font("title",size=20,color="black") + 
#   font("x.text", size = 20, color = "black") +
#   font("ylab", size = 20, color = "black") + 
#   font("y.text", size = 20, color = "black") +
#   stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
#                      label.y = 10.5)
# p <- base +
#   theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
# ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = xlist[2]
base <- ggboxplot(final.data, x=x, y="Pain",remove="Unknown",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
p
# ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = xlist[3]
base <- ggboxplot(final.data, x=x, y="Pain",remove="Unknown",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y=10.5)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
p
# ggsave(p, file=paste0(x,".pdf"),width=6, height=6)

x = "Occupation"
my_comparisons <- list( c("Employed", "Retired"), c("Retired", "Unemployed"), c("Employed", "Unemployed") )
base <- ggboxplot(final.data, x=x, y="Pain",remove="Unknown",
                  color = x, palette="jco",legend="none") +
  labs(x = NULL, y = "Pain", title = x) + 
  font("title",size=20,color="black") + 
  font("x.text", size = 20, color = "black") +
  font("ylab", size = 20, color = "black") + 
  font("y.text", size = 20, color = "black") +
  stat_compare_means(size=7, aes(label = "p.format"),show.legend=F,hide.ns=T,
                     label.y = 15) +
  stat_compare_means(comparisons = my_comparisons, aes(label = ..p.signif..),hide.ns=T)
p <- base +
  theme(plot.title=element_text(face="bold",size=20,margin=margin(t=10,b=20)))
p
# ggsave(p, file=paste0(x,".pdf"),width=6, height=6)
